Detecting Hate Speech with GPT-3

### 2021-03-23 outputs/documents/paper.Rmd
Fix one typo and save tex file

---
output: 
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: false
    toc: false
    fig_caption: true
    latex_engine: xelatex
    template: templates/svm-latex-ms.tex
bibliography: "references.bib"
header-includes:
  -  \usepackage{hyperref}
  -  \usepackage{amsmath}
biblio-style: apalike
title: "Detecting Hate Speech with GPT-3"
thanks: "Code and data are available at: https://github.com/kelichiu/GPT3-hate-speech-detection. We gratefully acknowledge the support of Gillian Hadfield and the Schwartz Reisman Institute for Technology and Society. We thank Amy Farrow, Haoluan Chen, Mauricio Vargas Sepúlveda, and Tom Davidson for helpful suggestions. Comments on the `r format(Sys.time(), '%d %B %Y')` version of this paper are welcome at: rohan.alexander@utoronto.ca."
author:
- name: Ke-Li Chiu
  affiliation: University of Toronto
- name: Rohan Alexander
  affiliation: University of Toronto and Schwartz Reisman Institute
abstract: "Sophisticated language models such as OpenAI's GPT-3 can generate hateful text that targets marginalized groups. Given this capacity, we are interested in whether large language models can be used to identify hate speech and classify text as sexist or racist? We use GPT-3 to identify sexist and racist text passages with zero-, one-, and few-shot learning. We find that with zero- and one-shot learning, GPT-3 is able to identify sexist or racist text with an accuracy between 48 per cent and 69 per cent. With few-shot learning and an instruction included in the prompt, the model's accuracy can be as high as 78 per cent. We conclude that large language models have a role to play in hate speech detection, and that with further development language models could be used to counter hate speech and even self-police."
keywords: "GPT-3; natural language processing; quantitative analysis; hate speech."
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
endnote: no
graphics: yes
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=80), echo = FALSE, warning = FALSE)
# library(dplyr)
library(tidyverse)
# library(tidyr)
# library(readr)
```

@@

In conclusion, with proper settings such as the inclusion of instruction and curated examples, large natural language models such as GPT-3 are capable of identifying sexist and racist text. However, it is possible that if a user intentionally misspells profane words, the models may be less likely to identify such content as problematic. This possibility deserves further investigation due to the tendency for language to change quickly. Furthermore, the models might classify texts that contain identity terms as problematic, as they are often associated with harmful text when being targeted. Various settings should be further explored to tackle these obstacles. To shed light why a text is misclassified, it might be appropriate to prompt GPT-3 to deliver an accompanying explanation for the decision, or to consider a larger dataset of sexist and racist content. The extent to which the identification and classification of hate speech can be explained is especially of interest for future work.

>>>>

---
output: 
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: true
    toc: false
    fig_caption: true
    latex_engine: xelatex
    template: templates/svm-latex-ms.tex
bibliography: "references.bib"
header-includes:
  -  \usepackage{hyperref}
  -  \usepackage{amsmath}
biblio-style: apalike
title: "Detecting Hate Speech with GPT-3"
thanks: "Code and data are available at: https://github.com/kelichiu/GPT3-hate-speech-detection. We gratefully acknowledge the support of Gillian Hadfield and the Schwartz Reisman Institute for Technology and Society. We thank Amy Farrow, Haoluan Chen, Mauricio Vargas Sepúlveda, and Tom Davidson for helpful suggestions. Comments on the `r format(Sys.time(), '%d %B %Y')` version of this paper are welcome at: rohan.alexander@utoronto.ca."
author:
- name: Ke-Li Chiu
  affiliation: University of Toronto
- name: Rohan Alexander
  affiliation: University of Toronto and Schwartz Reisman Institute
abstract: "Sophisticated language models such as OpenAI's GPT-3 can generate hateful text that targets marginalized groups. Given this capacity, we are interested in whether large language models can be used to identify hate speech and classify text as sexist or racist? We use GPT-3 to identify sexist and racist text passages with zero-, one-, and few-shot learning. We find that with zero- and one-shot learning, GPT-3 is able to identify sexist or racist text with an accuracy between 48 per cent and 69 per cent. With few-shot learning and an instruction included in the prompt, the model's accuracy can be as high as 78 per cent. We conclude that large language models have a role to play in hate speech detection, and that with further development language models could be used to counter hate speech and even self-police."
keywords: "GPT-3; natural language processing; quantitative analysis; hate speech."
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
endnote: no
graphics: yes
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=80), echo = FALSE, warning = FALSE)
# library(dplyr)
library(tidyverse)
# library(tidyr)
# library(readr)
```

@@

In conclusion, with proper settings such as the inclusion of instruction and curated examples, large natural language models such as GPT-3 are capable of identifying sexist and racist text. However, it is possible that if a user intentionally misspells profane words, the models may be less likely to identify such content as problematic. This possibility deserves further investigation due to the tendency for language to change quickly. Furthermore, the models might classify texts that contain identity terms as problematic, as they are often associated with harmful text when being targeted. Various settings should be further explored to tackle these obstacles. To shed light on why a text is misclassified, it might be appropriate to prompt GPT-3 to deliver an accompanying explanation for the decision, or to consider a larger dataset of sexist and racist content. The extent to which the identification and classification of hate speech can be explained is especially of interest for future work.
